---
title: "Analysis supporting: Are Critically Imperiled Six-Lined Racerunner Lizards Native or Introduced to Michigan?"
subtitle: "Project 3"
author: "Quinn Moon"
date: "04/30/2023"
output: html_document
---

Obviously youʻd have a bit more explanation to explain key points. This is just a skeleton

The code for this analysis is maintained in the following separate scripts and pulled in via codechunks: 

```{r }
#| cache = FALSE
knitr::read_chunk("allmapping.R")
knitr::read_chunk("discuss_figure.R")
knitr::read_chunk("discuss_map.R")
```

It would be good to put somehwere all of the packages one will need to install to get this to run. Even better in the readme. 

# Create a map of all sample locations

Load required packages. You might explain anything new or special about these. 

```{r, allmapping_pack}
#| message: FALSE
#| warning: FALSE 
```

Map all of the sample locations using... blah blah blah 

```{r, samplemap}
```

## plot the map and the sample points

Explain ... 

```{r, allmapping_pack}
#| message: FALSE
#| warning: FALSE 
```

# Discussion Figure

The goal here is to .. packages are... 
```{r, disc_fig_pack}
#| message: FALSE
#| warning: FALSE 
```

The data used are... 

```{r, disc_fig_data}
#| message: FALSE
#| warning: FALSE 
```

Plots are made with ggplot2:

```{r, disc_fig_plot}
```

And the phylogeny 

```{r, disc_fig_phylo}
```

# Discussion Map

The goal here is to .. packages are... 
```{r, disc_map_pack}
#| message: FALSE
#| warning: FALSE 
```

The data used are... 

```{r, disc_map_data}
#| message: FALSE
#| warning: FALSE 
```


Plots are made with ggplot2:

```{r, disc_map_plot}
```






